Existence of Forward Simulations for Particular Data Structures

### 2017-01-14 draftCAV/stack.tex
a pass on abstract implementations

As a consequence of Theorem~\ref{th:absImplStack} and Theorem~\ref{th:forSim}, $C\cup R\cup Com(pop)$-forward simulations are a sound and complete proof method for showing the correctness of a stack implementation with fixed pop commit points.

\begin{corollary}
A stack implementation $L$ with fixed pop commit points is a $C\cup R\cup Com(pop)$-refinement of $AbsS_0$ if{f} there exists a $C\cup R\cup Com(pop)$-forward simulation from $L$ to $AbsS$.
\end{corollary}

>>>>

As a consequence of Theorem~\ref{th:forSim}, $C\cup R\cup Com(pop)$-forward simulations are a sound and complete proof method for showing the correctness of a stack implementation with fixed pop commit points (up to the correctness of the commit points).

TODO EXPLAIN THAT THIS IS DIFFERENT W.R.T. QUEUES ($Abs_0$ doesn't have commit points).

\begin{corollary}
A stack implementation $L$ with fixed pop commit points is a $C\cup R\cup Com(pop)$-refinement of $AbsS$ if{f} there exists a $C\cup R\cup Com(pop)$-forward simulation from $L$ to $AbsS$.
\end{corollary}
